HBots

### 2020-12-21 HBtos/article/articleHBots.tex
anadiendo cambios en las figuras del articleHBots.tex

            \draw[thick,red]  (node cs: name =a ) -- (node cs:name =b);
            \draw[thick,blue] (node cs: name =a ) -- (node cs:name =c);
            \draw[thick,red] (node cs: name =b ) -- (node cs:name =d);
            \draw[thick,blue] (node cs: name =b ) -- (node cs:name =e);
            \draw[thick,red] (node cs: name =c ) -- (node cs:name =f);
            \draw[thick,blue] (node cs: name =c ) -- (node cs:name =g);

@@

            \draw[thick,red]  (node cs: name =a ) -- (node cs:name =b);
            \draw[thick,blue] (node cs: name =a ) -- (node cs:name =c);
            \draw[thick,red] (node cs: name =b ) -- (node cs:name =d);
            \draw[thick,blue] (node cs: name =b ) -- (node cs:name =e);
            \draw[thick,red] (node cs: name =c ) -- (node cs:name =f);
            \draw[thick,blue] (node cs: name =c ) -- (node cs:name =g);
            \draw[thick,black] (node cs: name =d ) -- (node cs:name =h);
            \draw[thick,red] (node cs: name =e ) -- (node cs:name =j);
            \draw[thick,red] (node cs: name =f ) -- (node cs:name =l);
            \draw[thick,red] (node cs: name =g) -- (node cs:name =n);
            \draw[thick,blue] (node cs: name =d ) -- (node cs:name =i);
            \draw[thick,blue] (node cs: name =e ) -- (node cs:name =k);
            \draw[thick,blue] (node cs: name =f) -- (node cs:name =m);
            \draw[thick,black] (node cs: name =g ) -- (node cs:name =o);

@@

    \subsubsection*{Turno 3.1}
    %TURNO 3 
    \begin{center}
        \begin{tikzpicture}

@@

            \draw[thick,red]  (node cs: name =a ) -- (node cs:name =b);
            \draw[thick,blue] (node cs: name =a ) -- (node cs:name =c);
            \draw[thick,red] (node cs: name =b ) -- (node cs:name =d);
            \draw[thick,blue] (node cs: name =b ) -- (node cs:name =e);
            \draw[thick,red] (node cs: name =c ) -- (node cs:name =f);
            \draw[thick,blue] (node cs: name =c ) -- (node cs:name =g);
            \draw[thick,blue] (node cs: name =d ) -- (node cs:name =h);
            \draw[thick,red] (node cs: name =e ) -- (node cs:name =i);
            \draw[thick,blue] (node cs: name =e ) -- (node cs:name =j);
            \draw[thick,red] (node cs: name =f) -- (node cs:name =k);
            \draw[thick,blue] (node cs: name =f ) -- (node cs:name =l);
            \draw[thick,red] (node cs: name =g ) -- (node cs:name =m);
            %\draw[thick,blue] (node cs: name =f) -- (node cs:name =m);
            %\draw[thick,black] (node cs: name =g ) -- (node cs:name =o);

@@

    \subsection*{Gr\'afica con niveles}

@@

            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =a ) -- (10,4);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =c ) -- (10,3);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =f ) -- (10,2);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =j ) -- (10,1);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =o ) -- (10,0);

            \node [right=5cm,text width=2cm] at (a)
            {
            \mbox{\Large n = 0}
            };

            \node [right=4cm,text width=2cm] at (c)
            {
            \mbox{\Large n = 1}
            };

            \node [right=3cm,text width=2cm] at (f)
            {
            \mbox{\Large n = 2}
            };

            \node [right=2cm,text width=2cm] at (j)
            {
            \mbox{\Large n = 3}
            };

            \node [right=1cm,text width=2cm] at (o)
            {
            \mbox{\Large n = 4}
            };

            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =a ) -- (4,5);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =b ) -- (3,4);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =d ) -- (2,3);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =g ) -- (1,2);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =k ) -- (0,1);

            \node [left=1cm,text width=1cm , rotate = -45] at (5,5)
            {
            \mbox{ k = 0}
            };

            \node [left=1cm,text width=1cm , rotate = -45] at (4,4)
            {
            \mbox{ k = 1}
            };

            \node [left=1cm,text width=1cm , rotate = -45] at (3,3)
            {
            \mbox{ k = 2}
            };

            \node [left=1cm,text width=1cm , rotate = -45] at (2,2)
            {
            \mbox{ k = 3}
            };

            \node [left=1cm,text width=1cm , rotate = -45] at (1,1)
            {
            \mbox{ k = 4}
            };

>>>>

            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red]  (node cs: name =a ) -- (node cs:name =b);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =a ) -- (node cs:name =c);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =b ) -- (node cs:name =d);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =b ) -- (node cs:name =e);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =c ) -- (node cs:name =f);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =c ) -- (node cs:name =g);

@@

            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red]  (node cs: name =a ) -- (node cs:name =b);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =a ) -- (node cs:name =c);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =b ) -- (node cs:name =d);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =b ) -- (node cs:name =e);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =c ) -- (node cs:name =f);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =c ) -- (node cs:name =g);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = black]},black] (node cs: name =d ) -- (node cs:name =h);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =e ) -- (node cs:name =j);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =f ) -- (node cs:name =l);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =g) -- (node cs:name =n);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =d ) -- (node cs:name =i);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =e ) -- (node cs:name =k);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =f) -- (node cs:name =m);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = black]},black] (node cs: name =g ) -- (node cs:name =o);

@@

    \subsubsection*{Turno 3.1}
    %Turno 3
    \begin{center}
        \begin{tikzpicture}

@@

            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red]  (node cs: name =a ) -- (node cs:name =b);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =a ) -- (node cs:name =c);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =b ) -- (node cs:name =d);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =b ) -- (node cs:name =e);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =c ) -- (node cs:name =f);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =c ) -- (node cs:name =g);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =d ) -- (node cs:name =h);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =e ) -- (node cs:name =i);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =e ) -- (node cs:name =j);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =f) -- (node cs:name =k);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =f ) -- (node cs:name =l);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =g ) -- (node cs:name =m);
            %\draw[thick,blue] (node cs: name =f) -- (node cs:name =m);
            %\draw[thick,black] (node cs: name =g ) -- (node cs:name =o);

@@

@@

            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =a ) -- (0,4);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =b ) -- (0,3);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =d ) -- (0,2);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =g ) -- (0,1);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =k ) -- (0,0);

            \node [left=4.1cm,text width=2cm] at (a)
            {
            \mbox{\Large n = 0}
            };

            \node [left=3.1,text width=2cm] at (b)
            {
            \mbox{\Large n = 1}
            };

            \node [left=2.1,text width=2cm] at (d)
            {
            \mbox{\Large n = 2}
            };

            \node [left=1.1,text width=2cm] at (g)
            {
            \mbox{\Large n = 3}
            };

            \node [left=0.1,text width=2cm] at (k)
            {
            \mbox{\Large n = 4}
            };

            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =a ) -- (6,5);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =c ) -- (7,4);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =f ) -- (8,3);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =j ) -- (9,2);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =o ) -- (10,1);

            \node [right=1cm,text width=1cm , rotate = 45] at (5,5)
            {
            \mbox{ k = 0}
            };

            \node [right=1cm,text width=1cm , rotate = 45] at (6,4)
            {
            \mbox{ k = 1}
            };

            \node [right=1cm,text width=1cm , rotate = 45] at (7,3)
            {
            \mbox{ k = 2}
            };

            \node [right=1cm,text width=1cm , rotate = 45] at (8,2)
            {
            \mbox{ k = 3}
            };

            \node [right=1cm,text width=1cm , rotate = 45] at (9,1)
            {
            \mbox{ k = 4}
            };
